---
title: ''
author: ''
date: ''
output: 
  html_document:
    df_print: paged
    keep_md: true
  word_document:
    reference_docx: style.1.docx
---

```{r setup, include = FALSE}

  knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE, 
                        fig.width  = 6 * 1.67, fig.height = 6)


# load("data/data.RData")
  source("scripts/01_data.R")
  source("scripts/functions.R")

  library(tidyverse)
  library(descr)
  library(viridis)
  library(RColorBrewer)
  library(flextable)
  library(knitr)
  library(pander)
  library(sjPlot)
  library(patchwork)
  library(survival)
  library(survminer)
  library(KMunicate)

  
```

# Descriptives

```{r time_lines}

  levs <- c("date_of_dx", "x1st_treatment", "relapse_1_progression",
            "relapse_2_progression", "relapse_3_progression", 
            "date_rip_last_f_up")

  labs <- c("Diagnosis", "First Tx", "First Relapse", "Second Relapse", 
            "Third Relapse", "End of Observation")

  times <- data %>%
    select(id, outcome, 
           date_of_dx, 
           relapse_1_progression, relapse_2_progression,
           relapse_3_progression, date_rip_last_f_up) %>%
    mutate(id = reorder(id, date_of_dx)) %>%
    gather(type, date, -id, -outcome) %>%
    mutate(type = factor(type, levels = levs, labels = labs))
  

```

Figure: Timing of key events for the `r length(unique(times$id))` patients. 
```{r time_line_plot}

  ggplot(times, aes(y = id, x = date, color = type)) +
    geom_point(size = 3, alpha = 0.5) +
    geom_line(data = filter(times, outcome == "Alive"),
              color = "grey", linetype = "dashed") +
    geom_line(data = filter(times, outcome != "Alive"),
              color = "grey") +
    scale_color_manual("", values = brewer.pal(9, "Set1")[c(1:5, 9)]) +
    theme(axis.text.y = element_blank(), 
          axis.ticks.y = element_blank(),
          strip.background = element_blank(),
          panel.grid = element_blank(), 
          panel.background = element_blank(), 
          legend.position = "bottom") +
    xlab("") +
    ylab("")

```
Dashed lines are patients that died; solid lines are patients that were alive at the last follow-up. 

Note: it stands out somewhat that there is not follow-up for the living patients up to the same date. 


Table 1. Sample characteristics (n = `r nrow(data)`)

```{r table1_describe}

  descript <- select(data, age_dx, gender, p53_exp, bcl2_percent,
                     outcome, dx_to_eos, pfs_outcome, dx_to_pfs)

  data_frame(
    Variable = name.1(descript),
    Observations = n.miss(descript),
    "Mean SD or n (%)" = summary.1(descript),
    "Median [IQR]" = med.iqr(descript),
    "(Min, Max)" = min.max(descript)
    ) %>% 
  flextable() 
  
```

Note: Missing one w/o a correct dx and/or EOS date. 

# OS

## KM plots

### Empty

```{r}

  sf <- survfit(Surv(dx_to_eos, died_flag) ~ 1, data = data) 

  pander(sf)

```

```{r}

  p1 <- ggsurvplot(
    sf, 
    data = data, 
    conf.int = TRUE, 
    surv.median.line = "hv", 
    risk.table = FALSE, 
    break.x.by = 26, 
    xlab = "Weeks"
    #xlim = c(0, lm)
    ) 

  p1$plot +  
    scale_color_discrete(guide = FALSE) 
  
```
  
```



### BCL2

```{r}

  sf <- survfit(Surv(dx_to_eos, died_flag) ~ bcl2_percent, data = data) 

  pander(sf)

```

```{r}

  p1 <- ggsurvplot(
    sf, 
    data = data, 
    conf.int = TRUE, 
    risk.table = TRUE, 
    break.x.by = 26, 
    xlab = "Weeks"
    #xlim = c(0, lm)
    ) 

  p1 
  
```


### P53

```{r}

  sf <- survfit(Surv(dx_to_eos, died_flag) ~ p53_exp, data = data) 

  pander(sf)

```

```{r}

  p1 <- ggsurvplot(
    sf, 
    data = data, 
    conf.int = TRUE, 
    risk.table = TRUE, 
    break.x.by = 26, 
    xlab = "Weeks"
    #xlim = c(0, lm)
    ) 

  p1 
  
```



### Cox models

```{r}

  os <- with(data, Surv(dx_to_eos, died_flag))

# ddist <- datadist(data) # For RMS
# options(datadist = "ddist")

  cox1 <- coxph(os ~  bcl2_percent,                             data = data)
  cox2 <- coxph(os ~                 p53_exp,                   data = data)
  cox3 <- coxph(os ~  bcl2_percent + p53_exp,                   data = data)
  cox4 <- coxph(os ~  bcl2_percent + p53_exp + gender + age_dx, data = data)

  tab_model(cox1, cox2, cox3, cox4, 
            dv.labels = c("BC12%", "P53", "Both", "+ Covariates"))

```

# PFS (first remission)

## KM plots

### Empty

```{r}

  sf <- survfit(Surv(dx_to_pfs, pfs_flag) ~ 1, data = data) 

  pander(sf)

```

```{r}

  p1 <- ggsurvplot(
    sf, 
    data = data, 
    conf.int = TRUE, 
    surv.median.line = "hv", 
    risk.table = FALSE, 
    break.x.by = 26, 
    xlab = "Weeks"
    #xlim = c(0, lm)
    ) 

  p1$plot +  
    scale_color_discrete(guide = FALSE) 
  
```

### BCL2

```{r}

  sf <- survfit(Surv(dx_to_pfs, pfs_flag) ~ bcl2_percent, data = data) 

  pander(sf)

```

```{r}

  p1 <- ggsurvplot(
    sf, 
    data = data, 
    conf.int = TRUE, 
    risk.table = TRUE, 
    break.x.by = 26, 
    xlab = "Weeks"
    #xlim = c(0, lm)
    ) 

  p1 
  
```

### P53

```{r}

  sf <- survfit(Surv(dx_to_pfs, pfs_flag) ~ p53_exp, data = data) 

  pander(sf)

```

```{r}

  p1 <- ggsurvplot(
    sf, 
    data = data, 
    conf.int = TRUE, 
    risk.table = TRUE, 
    break.x.by = 26, 
    xlab = "Weeks"
    #xlim = c(0, lm)
    ) 

  p1 
  
```

## Cox models

```{r}

  pfs <- with(data, Surv(dx_to_pfs, pfs_flag))

# ddist <- datadist(data) # For RMS
# options(datadist = "ddist")

  cox1 <- coxph(pfs ~  bcl2_percent,                             data = data)
  cox2 <- coxph(pfs ~                 p53_exp,                   data = data)
  cox3 <- coxph(pfs ~  bcl2_percent + p53_exp,                   data = data)
  cox4 <- coxph(pfs ~  bcl2_percent + p53_exp + gender + age_dx, data = data)

  tab_model(cox1, cox2, cox3, cox4, 
            dv.labels = c("BC12%", "P53", "Both", "+ Covariates"))

```



```{r code_book}

#  print(summarytools::dfSummary(data), method = "render")

```

```{r sysinfo}

  DescTools::SysInfo()

```



